\emph{Light Exposure Behavior Assessment (LEBA)}: Development of a novel instrument to capture light exposure-related behaviours

### 2022-01-08 manuscript.Rmd
Figure Legends are added

                    4[label = <Confirmatory Factor Analysis<br/>on the Five Factor Model (23 Items; n=262)<br/>Acceptable Fit ( CFI = .97; TLI= .96; RMSEA = .04, SRMR = .09)>]
                     5[label = <Reliability Analysis on CFA (23 Items; n=262)<br/>Ordinal alpha F1=.93; F2=.83; F3 =.70; F4=.69; F5=.52<br/>Mcdonald  omega(total) for the total scale = .73>]
                    8[label = <Measurement Invariance Analysis<br/>Residual measurement invariance achieved>]
                    9[label = 'Semantic Analysis']
                    10[label = <LEBA Short Form (18 Items; n=690)<br/>Based on Item Response Theory>]
                    }
                subgraph cluster_2 {
                      graph[fontname = Helvetica,shape = rectangle]
                      style = rounded
                     node[fontname = Helvetica, margin = 0.2,width = 18, height = 2.5, 
                fixedsize = true, fontsize = 45 ]
                    6[label = 
                    <6-Factor solution:<br/>one factor emerged with only two salient loadings>
                    ]
                    7[label = 'Rejected']
                    }

@@

```{r figCor, out.height="150%",out.width="100%",fig.cap= "Correlation plot of the items",results='asis', fig.align='center'}

@@

write.csv(full.map, "Table_raw/map_stat")
```
Scree plot ( Figure \@ref(fig:facIdFig)) suggested a six-factor solution. Horn's parallel analysis [@hornRationaleTestNumber1965] with 500 iterations also indicated a six-factor solution. However, the minimum average partial (MAP) method (Table \@ref(tab:factormp)) [@velicerDeterminingNumberComponents1976] and Hull method [@lorenzo-sevaHullMethodSelecting2011] ( Figure \@ref(fig:facIdFig)) suggested a five-factor solution. As a result, we tested both five-factor and six-factor solutions.
```{r factors, include=F}
fator <- cowplot::plot_grid(parallel, scree.plot,Hull, 
                   labels = "AUTO",
                   ncol=1, 
                  align = "v", 
                  label_size = 12,
                  label_fontfamily = "Arial",
                  label_fontface = "plain")
ggsave("Manuscript.figures/factors.png",fator, width = 6, height = 12, dpi = 1200)
```

```{r facIdFig, out.height="100%", out.width="100%",fig.align='center', fig.cap='Factor Identification (A) Parallel analysis (B) Scree Plot (C) Hull Method',  warning=FALSE, results= 'asis'}

@@

p1 <- ggplot2::ggplot() + ggplot2::annotation_custom(grid::rasterGrob(img1,
                                                                      width=NULL,
                                                                      height=NULL),
                                                     -Inf, Inf, -Inf, Inf)+apatheme

EFAplot.1 <- plot_grid(
 p1, residual.plot,
  labels = "AUTO",
  align="h",
  ncol = 2,
  label_size = 12,
  label_fontfamily = "Arial",
  label_fontface = "plain",
  label_y = .99,
  label_x = .04
)

ggsave("Manuscript.figures/EFAfull.png",EFAplot.1, width = 10, height =10, dpi = 1200)

@@

```{r EFAplot, fig.align='center', fig.cap='(A) Five Factor Solution obtained in Exploratory Factor Analysis (B) Histogram of nonredundent residula correlations', warning=FALSE,  results='asis'}

@@

```{r CFA23withMI, include=FALSE}
LB.model.Cor.2 <- "F1 =~ a1*item16 + item36 + a2*item17
                 F2 =~ item11 + item10 + item12+ item07+ Ritem08+ item09
                 F3 =~  item27+ item03+ item40 + item30 + item41
                 F4 =~ a3*item32 + item35 + item38+ a4*item33 
                 F5 =~ item46+ item45+ item25+ item04+ item01 
                       a1==a2
                       a3==a4
                item30 ~~  item41
                       "

@@

```{r figcfa, fig.cap = "Five Factor CFA Model of LEBA", out.height="150%", out.width="100%", dpi=1200,  warning=FALSE}
#library(semPlot)

semPaths (fit.Cor.2 , 
          what= "std",
          #"hide", #(hides coefficeits)
          #whatLabels = "std",
          intercepts = F,
          style ="lisrel",
          #residScale = 6,
          theme = "colorblind",
          nCharNodes = 0,
          reorder =T,
          rotation =2,
          layout ="tree",
          cardinal = T,
          curvePivot =T,
          sizeMan =6,#items length
          sizeMan2 = 2,#items
          sizeLat = 12,#factors
          thresholds = FALSE,
          equalizeManifests =F,
          fade = FALSE,
          edge.label.cex = .8,
          exoCov = FALSE,
          centerLevels = T,
          #edge.color="black",
          label.scale=T,
          label.cex=1, #Font of factor and item name
          residuals=FALSE,
           exoVar=FALSE,
          fixedStyle=6, #Style of arrow (guide item)
          freeStyle=1#Style of arrow (other item), #XKCD = TRUE

@@

## GGplot2 item-info
###F1
F1.iteminfo.1 <- ggplot(F1.item.info.data , aes(x=Theta, y=F1.item.info.1)) +
  geom_line()  +apatheme +labs(y="Item Information", title = "F1 item16") + geom_hline(yintercept = .20, colour ="red")
F1.iteminfo.2 <- ggplot(F1.item.info.data , aes(x=Theta, y=F1.item.info.2)) +
  geom_line()  +apatheme +labs(y="Item Information", title = "F1 item36")+geom_hline(yintercept = .20, colour ="red")
F1.iteminfo.3 <- ggplot(F1.item.info.data , aes(x=Theta, y=F1.item.info.3)) +
  geom_line()  +apatheme +labs(y="Item Information", title = "F1 item17")+ylim(0,6)+geom_hline(yintercept = .20, colour ="red")

@@

F2.iteminfo.1 <- ggplot(F2.item.info.data , aes(x=Theta, y=F2.item.info.1)) +
  geom_line()  +apatheme +labs(y="Item Information", title = "F2 item11")+ylim(0,3)+geom_hline(yintercept = .20, colour ="red")

F2.iteminfo.2 <- ggplot(F2.item.info.data , aes(x=Theta, y=F2.item.info.2)) +
  geom_line()  + apatheme +
  labs(y="Item Information", title = "F2 item10")+
  ylim(0,3)+geom_hline(yintercept = .20, colour ="red")

F2.iteminfo.3 <- ggplot(F2.item.info.data , aes(x=Theta, y=F2.item.info.3)) +
  geom_line()  +apatheme +
  labs(y="Item Information", title = "F2 item12")+
  ylim(0,3)+geom_hline(yintercept = .20, colour ="red")

F2.iteminfo.4 <- ggplot(F2.item.info.data , aes(x=Theta, y=F2.item.info.4)) +
  geom_line()  +apatheme +
  labs(y="Item Information", title = "F2 item07")+ylim(0,3)+
  geom_hline(yintercept = .20, colour ="red")

F2.iteminfo.5 <- ggplot(F2.item.info.data , aes(x=Theta, y=F2.item.info.5)) +
  geom_line()  +apatheme +
  labs(y="Item Information", title = "F2 item08")+ylim(0,3)+
  geom_hline(yintercept = .20, colour ="red")

F2.iteminfo.6 <- ggplot(F2.item.info.data , aes(x=Theta, y=F2.item.info.6)) +
  geom_line()  +apatheme +
  labs(y="Item Information", title = "F2 item09")+ylim(0,3)+
  geom_hline(yintercept = .20, colour ="red")

###F3
F3.iteminfo.1 <- ggplot(F3.item.info.data , aes(x=Theta, y=F3.item.info.1)) +
  geom_line()  +apatheme +labs(y="Item Information", title = "F3 item27")+
  ylim(0,3)+geom_hline(yintercept = .20, colour ="red")

F3.iteminfo.2 <- ggplot(F3.item.info.data , aes(x=Theta, y=F3.item.info.2)) +
  geom_line()  +apatheme +
  labs(y="Item Information",title = "F3 item03")+
  ylim(0,3)+geom_hline(yintercept = .20, colour ="red")

F3.iteminfo.3 <- ggplot(F3.item.info.data , aes(x=Theta, y=F3.item.info.3)) +
  geom_line()  +apatheme +
  labs(y="Item Information",title = "F3 item40")+
  ylim(0,3)+geom_hline(yintercept = .20, colour ="red")

F3.iteminfo.4 <- ggplot(F3.item.info.data , aes(x=Theta, y=F3.item.info.4)) +
  geom_line()  +apatheme +
  labs(y="Item Information",title = "F3 item30")+
  ylim(0,3)+geom_hline(yintercept = .20, colour ="red")

F3.iteminfo.5 <- ggplot(F3.item.info.data , aes(x=Theta, y=F3.item.info.5)) +
  geom_line()  +apatheme +
  labs(y="Item Information", title = "F3 item41")+
  ylim(0,3)+geom_hline(yintercept = .20, colour ="red")

@@

F4.iteminfo.1 <- ggplot(F4.item.info.data , aes(x=Theta, y=F4.item.info.1)) +
  geom_line()  +apatheme +labs(y="Item Information", title = "F4 item32")+
  ylim(0,3)+geom_hline(yintercept = .20, colour ="red")

F4.iteminfo.2 <- ggplot(F4.item.info.data , aes(x=Theta, y=F4.item.info.2)) +
  geom_line()  +apatheme +
  labs(y="Item Information",title = "F4 item35")+
  ylim(0,3)+geom_hline(yintercept = .20, colour ="red")

F4.iteminfo.3 <- ggplot(F4.item.info.data , aes(x=Theta, y=F4.item.info.3)) +
  geom_line()  +apatheme +
  labs(y="Item Information",title = "F4 item38")+
  ylim(0,3)+geom_hline(yintercept = .20, colour ="red")

F4.iteminfo.4 <- ggplot(F4.item.info.data , aes(x=Theta, y=F4.item.info.4)) +
  geom_line()  +apatheme +
  labs(y="Item Information",title = "F4 item33")+geom_hline(yintercept = .20, colour ="red")

@@

F5.iteminfo.1 <- ggplot(F3.item.info.data , aes(x=Theta, y=F5.item.info.1)) +
  geom_line()  +apatheme +labs(y="Item Information", title = "F5 item46")+
  ylim(0,3)+geom_hline(yintercept = .20, colour ="red")

F5.iteminfo.2 <- ggplot(F3.item.info.data , aes(x=Theta, y=F5.item.info.2)) +
  geom_line()  +apatheme +
  labs(y="Item Information",title = "F5 item45")+
  ylim(0,3)+geom_hline(yintercept = .20, colour ="red")

F5.iteminfo.3 <- ggplot(F3.item.info.data , aes(x=Theta, y=F5.item.info.3)) +
  geom_line()  +apatheme +
  labs(y="Item Information",title = "F5 item25")+
  ylim(0,3)+geom_hline(yintercept = .20, colour ="red")

F5.iteminfo.4 <- ggplot(F3.item.info.data , aes(x=Theta, y=F5.item.info.4)) +
  geom_line()  +apatheme +
  labs(y="Item Information",title = "F5 item04")+
 geom_hline(yintercept = .20, colour ="red")

F5.iteminfo.5 <- ggplot(F3.item.info.data , aes(x=Theta, y=F5.item.info.5)) +
  geom_line()  +apatheme +
  labs(y="Item Information", title = "F5 item01")+
  ylim(0,3)+geom_hline(yintercept = .20, colour ="red")

@@

F1.itemplots <- cowplot::plot_grid(F1.iteminfo.1,F1.iteminfo.2, F1.iteminfo.3,
                   labels = "AUTO",
                     align="v",
                     ncol = 2,
                     label_size = 12,
                     label_fontfamily = "serif",
                     label_fontface = "plain")
ggsave("Manuscript.figures/F1.itemplots.png",F1.itemplots, width = 10, height = 12, dpi = 600,bg = "white")

F2.itemplots <- cowplot::plot_grid(F2.iteminfo.1,F2.iteminfo.2, F2.iteminfo.3,
                                   F2.iteminfo.4,F2.iteminfo.5,F2.iteminfo.6,
                   labels = "AUTO",
                     align="v",
                     ncol = 2,
                     label_size = 12,
                     label_fontfamily = "serif",
                     label_fontface = "plain")
ggsave("Manuscript.figures/F2.itemplots.png",F2.itemplots, width = 10, height = 12, dpi = 1200, bg = "white")

F3.itemplots <- cowplot::plot_grid(F3.iteminfo.1,F3.iteminfo.2, F3.iteminfo.3,
                                   F3.iteminfo.4,F3.iteminfo.5,
                 labels = "AUTO",
                     align="v",
                     ncol = 2,
                     label_size = 12,
                     label_fontfamily = "serif",
                     label_fontface = "plain")
ggsave("Manuscript.figures/F3.itemplots.png",F3.itemplots, width = 10, height = 12, dpi = 1200,bg = "white")

F4.itemplots <- cowplot::plot_grid(F4.iteminfo.1,F4.iteminfo.2, F4.iteminfo.3,
                                   F4.iteminfo.4,
                   labels = "AUTO",
                     align="v",
                     ncol = 2,
                     label_size = 12,
                     label_fontfamily = "serif",
                     label_fontface = "plain")
ggsave("Manuscript.figures/F4.itemplots.png",F4.itemplots, width = 10, height = 12, dpi = 1200,bg = "white")

F5.itemplots <- cowplot::plot_grid(F5.iteminfo.1,F5.iteminfo.2, F5.iteminfo.3,
                                   F5.iteminfo.4,F5.iteminfo.5,
                   labels = "AUTO",
                     align="v",
                     ncol = 2,
                     label_size = 12,
                     label_fontfamily = "serif",
                     label_fontface = "plain")
ggsave("Manuscript.figures/F5.itemplots.png",F5.itemplots, width = 10, height = 12, dpi = 1200, bg = "white")
```

@@

F1.tic <- ggplot(F1.test.data, aes(x=Theta, y=F1.T1)) +
  geom_line()+apatheme+
  labs(y="Test Information", title = "F1 Test Inforfamtion")

@@

TIC <- cowplot::plot_grid(F1.tic,F2.tic, F3.tic,
                                   F4.tic,F5.tic,
                   labels = "AUTO",
                     align="v",
                     ncol = 2,
                     label_size = 12,
                     label_fontfamily = "serif",
                     label_fontface = "plain")
ggsave("Manuscript.figures/TIC.png",TIC, width = 10, height = 12, dpi = 1200, bg = "white")

@@

```{r perfit, include=F}
personfit <- plot_grid(F1.person, F2.person,F3.person,F4.person,F5.person, 
          labels = "AUTO", label_size = 12,align = "v", ncol =2,
                       label_fontfamily = "serif",
                     label_fontface = "plain")

>>>>

                    4[label = <Confirmatory Factor Analysis<br/>on the Five Factor Model (23 Items; n=262)<br/>Acceptable Fit ( CFI = .97; TLI= .96; RMSEA = .04, SRMR = .09)>]
                     5[label = <Reliability Analysis (23 Items; n=262)<br/>Ordinal alpha F1=.93; F2=.83; F3 =.70; F4=.69; F5=.52<br/>Mcdonald  omega(total) for the total scale = .73>]
                    8[label = <Measurement Invariance Analysis<br/>Residual measurement invariance achieved>]
                    9[label = 'Semantic Analysis']
                    10[label = <LEBA Short Form (18 Items; n=690)<br/>Based on Item Response Theory>]
                    }
                subgraph cluster_2 {
                      graph[fontname = Helvetica,shape = rectangle]
                      style = rounded
                     node[fontname = Helvetica, margin = 0.2,width = 18, height = 2.5, 
                fixedsize = true, fontsize = 45 ]
                    6[label = 
                    <6-Factor solution:<br/>one factor emerged with only two salient loadings>
                    ]
                    7[label = 'Rejected']
                    }

@@

```{r figCor, out.height="150%",out.width="100%",fig.cap= "Inter item ploychroric correlationc coefficients for the 48 items. The red gradient indicates negative correlations, white indicates zero correlation and the blue gradient indicate positive correlations. 4.9% inter-item correlation coefficients were higher than .30 ",results='asis', fig.align='center'}

@@

write.csv(full.map, "Table_raw/map_stat")
```
Scree plot ( Figure \@ref(fig:facIdFig)) suggested a six-factor solution. Horn's parallel analysis [@hornRationaleTestNumber1965] with 500 iterations also indicated a six-factor solution. However, the minimum average partial (MAP) method (Table \@ref(tab:factormp)) [@velicerDeterminingNumberComponents1976] and Hull method [@lorenzo-sevaHullMethodSelecting2011] ( Figure \@ref(fig:facIdFig)) suggested a five-factor solution. As a result, we tested both five-factor and six-factor solutions.
```{r factors, include=F}
fator <- cowplot::plot_grid(parallel, scree.plot,Hull, 
                   labels = "AUTO",
                   ncol=1, 
                  align = "v", 
                  label_size = 15,
                  label_fontfamily = "Arial",
                  label_fontface = "plain")
ggsave("Manuscript.figures/factors.png",fator, width = 6, height = 12, dpi = 1200)
```

```{r facIdFig, out.height="100%", out.width="100%",fig.align='center', fig.cap='Factor Identification Methods (A) In parallel analysis we drew 500 sets of random data with the same number of participants as our orihinal data (n=428) and adjusted the mean eigenvalues for sample bias. In x-axis we plotted the number of possible factors and in y axis we plotted the mean ajusted eigenvalues. The First inflection point of the plot indicated the optimal number of factor was six. re  (B) In the scree scree plot possible numner of factors are plotted againest obtained eigen values. Scree plot suggested six factors. (C) In Hull method we plotted the number of posible factors in the x axis and in the y axis we ploed the CAF index(CAF: Common Part Accounted for-an indicator of model fit). Hull method indicated 5 factors are requied to  balance model fit and the number of parameters ',  warning=FALSE, results= 'asis'}

@@

p1 <- ggplot2::ggplot() + ggplot2::annotation_custom(grid::rasterGrob(img1,
                                                                      width=.4,
                                                                      height=.8),
                                                     -Inf, Inf, -Inf, Inf)+
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank())
        #text=element_text(family = "Helvetica"))

EFAplot.1 <- plot_grid(
 p1, residual.plot,
  labels = "AUTO",
  align="h",
  ncol = 1,
  label_size = 15,
  label_fontfamily = "Arial",
  label_fontface = "plain",
  label_y = .99,
  label_x = .02,
 rel_heights = c(1.5,1)
)

ggsave("Manuscript.figures/EFAfull.png",EFAplot.1, width = 4, height =8, dpi = 1200, bg ="white")

@@

```{r EFAplot, fig.align='center', fig.cap='(A) Five Factor Solution obtained in Exploratory Factor Analysis. The factor loadings ranged between .49-.99 (B) Histogram of nonredundent residula correlations indicated 26% correlations are higher than absolute value of .05 indicating a possible under factoring', warning=FALSE,  results='asis'}

@@

```{r CFA23withMI, include=FALSE}
LB.model.Cor.2 <- "F1 =~ a1*item16 + item36 + a2*item17
                 F2 =~ item11 + item10 + item12+ item07+ Ritem08+ item09
                 F3 =~  item27+ item03+ item40 + item30 + item41
                 F4 =~ a3*item32 + item35 + item38+ a4*item33 
                 F5 =~ item46+ item45+ item25+ item04+ item01 
                       a1==a2
                       a3==a4
                item30 ~~  item41
                     F1 ~~ 0*F2
F1 ~~ 0*F3
F1 ~~ 0*F4
F1 ~~ 0*F5
F2 ~~ 0*F3
F2 ~~ 0*F4
F2 ~~ 0*F5
F3 ~~ 0*F4
F3 ~~ 0*F5
F4 ~~ 0*F5"

@@

```{r figcfa, fig.cap = "Five Factor  Model of LEBA obtained by Confirmatory Factor Analysis. By allowing item pain 41 & 30 to covary their error variance our model attained the best fit.", out.height="150%", out.width="100%", dpi=1200,  warning=FALSE}
#library(semPlot)

semPaths (fit.Cor.2 , 
          what= "std",
          #"hide", #(hides coefficeits)
          #whatLabels = "std",
          intercepts = F,
          style ="lisrel",
          #residScale = 6,
          theme = "colorblind",
          nCharNodes = 0,
          reorder =T,
          rotation =2,
          layout ="tree",
          cardinal = T,
          curvePivot =T,
          sizeMan =6,#items length
          sizeMan2 = 2,#items
          sizeLat = 12,#factors
          thresholds = FALSE,
          equalizeManifests =F,
          fade = FALSE,
          edge.label.cex = .8,
          exoCov = T,
          centerLevels = T,
          #edge.color="black",
          label.scale=T,
          label.cex=1, #Font of factor and item name
          residuals=FALSE,
           exoVar=FALSE,
          fixedStyle=6, #Style of arrow (guide item)
          freeStyle=1#Style of arrow (other item), #XKCD = TRUE

@@

## GGplot2 item-info
###F1
F1.iteminfo.1 <- ggplot(F1.item.info.data , aes(x=Theta, y=F1.item.info.1)) +
  geom_line()  +apatheme +labs(y="Item Information", title = "F1 item16") + geom_hline(yintercept = .18, colour ="red")
F1.iteminfo.2 <- ggplot(F1.item.info.data , aes(x=Theta, y=F1.item.info.2)) +
  geom_line()  +apatheme +labs(y="Item Information", title = "F1 item36")+geom_hline(yintercept = .18, colour ="red")
F1.iteminfo.3 <- ggplot(F1.item.info.data , aes(x=Theta, y=F1.item.info.3)) +
  geom_line()  +apatheme +labs(y="Item Information", title = "F1 item17")+ylim(0,6)+geom_hline(yintercept = .18, colour ="red")

@@

F2.iteminfo.1 <- ggplot(F2.item.info.data , aes(x=Theta, y=F2.item.info.1)) +
  geom_line()  +apatheme +labs(y="Item Information", title = "F2 item11")+ylim(0,3)+geom_hline(yintercept = .18, colour ="red")

F2.iteminfo.2 <- ggplot(F2.item.info.data , aes(x=Theta, y=F2.item.info.2)) +
  geom_line()  + apatheme +
  labs(y="Item Information", title = "F2 item10")+
  ylim(0,3)+geom_hline(yintercept = .18, colour ="red")

F2.iteminfo.3 <- ggplot(F2.item.info.data , aes(x=Theta, y=F2.item.info.3)) +
  geom_line()  +apatheme +
  labs(y="Item Information", title = "F2 item12")+
  ylim(0,3)+geom_hline(yintercept = .18, colour ="red")

F2.iteminfo.4 <- ggplot(F2.item.info.data , aes(x=Theta, y=F2.item.info.4)) +
  geom_line()  +apatheme +
  labs(y="Item Information", title = "F2 item07")+ylim(0,3)+
  geom_hline(yintercept = .18, colour ="red")

F2.iteminfo.5 <- ggplot(F2.item.info.data , aes(x=Theta, y=F2.item.info.5)) +
  geom_line()  +apatheme +
  labs(y="Item Information", title = "F2 item08")+ylim(0,3)+
  geom_hline(yintercept = .18, colour ="red")

F2.iteminfo.6 <- ggplot(F2.item.info.data , aes(x=Theta, y=F2.item.info.6)) +
  geom_line()  +apatheme +
  labs(y="Item Information", title = "F2 item09")+ylim(0,3)+
  geom_hline(yintercept = .18, colour ="red")

###F3
F3.iteminfo.1 <- ggplot(F3.item.info.data , aes(x=Theta, y=F3.item.info.1)) +
  geom_line()  +apatheme +labs(y="Item Information", title = "F3 item27")+
  ylim(0,3)+geom_hline(yintercept = .18, colour ="red")

F3.iteminfo.2 <- ggplot(F3.item.info.data , aes(x=Theta, y=F3.item.info.2)) +
  geom_line()  +apatheme +
  labs(y="Item Information",title = "F3 item03")+
  ylim(0,3)+geom_hline(yintercept = .18, colour ="red")

F3.iteminfo.3 <- ggplot(F3.item.info.data , aes(x=Theta, y=F3.item.info.3)) +
  geom_line()  +apatheme +
  labs(y="Item Information",title = "F3 item40")+
  ylim(0,3)+geom_hline(yintercept = .18, colour ="red")

F3.iteminfo.4 <- ggplot(F3.item.info.data , aes(x=Theta, y=F3.item.info.4)) +
  geom_line()  +apatheme +
  labs(y="Item Information",title = "F3 item30")+
  ylim(0,3)+geom_hline(yintercept = .18, colour ="red")

F3.iteminfo.5 <- ggplot(F3.item.info.data , aes(x=Theta, y=F3.item.info.5)) +
  geom_line()  +apatheme +
  labs(y="Item Information", title = "F3 item41")+
  ylim(0,3)+geom_hline(yintercept = .18, colour ="red")

@@

F4.iteminfo.1 <- ggplot(F4.item.info.data , aes(x=Theta, y=F4.item.info.1)) +
  geom_line()  +apatheme +labs(y="Item Information", title = "F4 item32")+
  ylim(0,3)+geom_hline(yintercept = .18, colour ="red")

F4.iteminfo.2 <- ggplot(F4.item.info.data , aes(x=Theta, y=F4.item.info.2)) +
  geom_line()  +apatheme +
  labs(y="Item Information",title = "F4 item35")+
  ylim(0,3)+geom_hline(yintercept = .18, colour ="red")

F4.iteminfo.3 <- ggplot(F4.item.info.data , aes(x=Theta, y=F4.item.info.3)) +
  geom_line()  +apatheme +
  labs(y="Item Information",title = "F4 item38")+
  ylim(0,3)+geom_hline(yintercept = .18, colour ="red")

F4.iteminfo.4 <- ggplot(F4.item.info.data , aes(x=Theta, y=F4.item.info.4)) +
  geom_line()  +apatheme +
  labs(y="Item Information",title = "F4 item33")+geom_hline(yintercept = .18, colour ="red")

@@

F5.iteminfo.1 <- ggplot(F3.item.info.data , aes(x=Theta, y=F5.item.info.1)) +
  geom_line()  +apatheme +labs(y="Item Information", title = "F5 item46")+
  ylim(0,2)+geom_hline(yintercept = .18, colour ="red")

F5.iteminfo.2 <- ggplot(F3.item.info.data , aes(x=Theta, y=F5.item.info.2)) +
  geom_line()  +apatheme +
  labs(y="Item Information",title = "F5 item45")+
  ylim(0,2)+geom_hline(yintercept = .18, colour ="red")

F5.iteminfo.3 <- ggplot(F3.item.info.data , aes(x=Theta, y=F5.item.info.3)) +
  geom_line()  +apatheme +
  labs(y="Item Information",title = "F5 item25")+
  ylim(0,2)+geom_hline(yintercept = .18, colour ="red")

F5.iteminfo.4 <- ggplot(F3.item.info.data , aes(x=Theta, y=F5.item.info.4)) +
  geom_line()  +apatheme +
  labs(y="Item Information",title = "F5 item04")+
 geom_hline(yintercept = .18, colour ="red")+ylim(0,2)

F5.iteminfo.5 <- ggplot(F3.item.info.data , aes(x=Theta, y=F5.item.info.5)) +
  geom_line()  +apatheme +
  labs(y="Item Information", title = "F5 item01")+
  ylim(0,2)+geom_hline(yintercept = .18, colour ="red")

@@

F1.itemplots <- cowplot::plot_grid(F1.iteminfo.1,F1.iteminfo.2, F1.iteminfo.3,
                   labels = "AUTO",
                     align="v",
                     ncol = 2,
                     label_size = 12,
                     label_fontfamily = "Arial",
  label_fontface = "plain")
ggsave("Manuscript.figures/F1.itemplots.png",F1.itemplots, width = 10, height = 12, dpi = 600,bg = "white")

F2.itemplots <- cowplot::plot_grid(F2.iteminfo.1,F2.iteminfo.2, F2.iteminfo.3,
                                   F2.iteminfo.4,F2.iteminfo.5,F2.iteminfo.6,
                   labels = "AUTO",
                     align="v",
                     ncol = 2,
                     label_size = 12,
                     label_fontfamily = "Arial",
                     label_fontface = "plain")
ggsave("Manuscript.figures/F2.itemplots.png",F2.itemplots, width = 10, height = 12, dpi = 1200, bg = "white")

F3.itemplots <- cowplot::plot_grid(F3.iteminfo.1,F3.iteminfo.2, F3.iteminfo.3,
                                   F3.iteminfo.4,F3.iteminfo.5,
                 labels = "AUTO",
                     align="v",
                     ncol = 2,
                     label_size = 12,
                     label_fontfamily = "Arial",
                     label_fontface = "plain")
ggsave("Manuscript.figures/F3.itemplots.png",F3.itemplots, width = 10, height = 12, dpi = 1200,bg = "white")

F4.itemplots <- cowplot::plot_grid(F4.iteminfo.1,F4.iteminfo.2, F4.iteminfo.3,
                                   F4.iteminfo.4,
                   labels = "AUTO",
                     align="v",
                     ncol = 2,
                     label_size = 12,
                     label_fontfamily = "Arial",
                     label_fontface = "plain")
ggsave("Manuscript.figures/F4.itemplots.png",F4.itemplots, width = 10, height = 12, dpi = 1200,bg = "white")

F5.itemplots <- cowplot::plot_grid(F5.iteminfo.1,F5.iteminfo.2, F5.iteminfo.3,
                                   F5.iteminfo.4,F5.iteminfo.5,
                   labels = "AUTO",
                     align="v",
                     ncol = 2,
                     label_size = 12,
                     label_fontfamily = "Arial",
                     label_fontface = "plain")
ggsave("Manuscript.figures/F5.itemplots.png",F5.itemplots, width = 10, height = 12, dpi = 1200, bg = "white")
```

```{r inteminfoggplo2com, eval=FALSE, include=FALSE}
#Victimization
pacman::p_load(reshape,ggsci)
Theta <- matrix(seq(-6,6, by = .1))

##Item Info
Item16 <- iteminfo(F1.item1, Theta)
Item36 <- iteminfo(F1.item2, Theta)
Item17 <- iteminfo(F1.item3, Theta)
Item11 <- iteminfo(F2.item1, Theta)
Item10 <- iteminfo(F2.item2, Theta)
Item12 <- iteminfo(F2.item3, Theta)
Item07 <- iteminfo(F2.item4, Theta)
Item08 <- iteminfo(F2.item5, Theta)
Item09 <- iteminfo(F2.item6, Theta)
Item27 <- iteminfo(F3.item1, Theta)
Item03 <- iteminfo(F3.item2, Theta)
Item40 <- iteminfo(F3.item3, Theta)
Item30 <- iteminfo(F3.item4, Theta)
Item41 <- iteminfo(F3.item5, Theta)
Item32 <- iteminfo(F4.item1, Theta)
Item35 <- iteminfo(F4.item2, Theta)
Item38 <- iteminfo(F4.item3, Theta)
Item33 <- iteminfo(F4.item4, Theta)
Item46 <- iteminfo(F5.item1, Theta)
Item45 <- iteminfo(F5.item2, Theta)
Item25 <- iteminfo(F5.item3, Theta)
Item04 <- iteminfo(F5.item4, Theta)
Item01 <- iteminfo(F5.item5, Theta)

F1.item.info.data <- as.data.frame(cbind(Item16, 
                                              Item36,
                                              Item17))

F2.item.info.data <- as.data.frame(cbind(Item11, 
                                              Item10,
                                              Item12,
                                         Item07,
                                         Item08,
                                         Item09))

F3.item.info.data <- as.data.frame(cbind(Item27, 
                                              Item03,
                                              Item40,
                                         Item30,
                                        Item41))

F4.item.info.data <- as.data.frame(cbind(Item32, 
                                              Item35,
                                              Item38,
                                         Item33))
F5.item.info.data <- as.data.frame(cbind(Item46, 
                                              Item45,
                                             Item25,
                                         Item04,
                                         Item01))

F1.item.info.data.long <- melt(F1.item.info.data)
F2.item.info.data.long <- melt(F2.item.info.data)
F3.item.info.data.long <- melt(F3.item.info.data)
F4.item.info.data.long <- melt(F4.item.info.data)
F5.item.info.data.long <- melt(F5.item.info.data)

F1.item.info.data.2 <- data.frame(Theta=seq(-6,6, by = .1), F1.item.info.data.long)
F2.item.info.data.2 <- data.frame(Theta=seq(-6,6, by = .1), F2.item.info.data.long)
F3.item.info.data.2 <- data.frame(Theta=seq(-6,6, by = .1), F3.item.info.data.long)
F4.item.info.data.2 <- data.frame(Theta=seq(-6,6, by = .1), F4.item.info.data.long)
F5.item.info.data.2 <- data.frame(Theta=seq(-6,6, by = .1), F5.item.info.data.long)

F1.iic2 <- ggplot(F1.item.info.data.2,aes(Theta,value,col=variable))+geom_line()+apatheme+
  ggtitle("F1 Item Information Plot")+theme(legend.position = "none")+
  labs(y = "Item Information")+facet_wrap(~variable)+theme(strip.text.x = element_text(size = 15))+
  scale_color_npg()+geom_hline(yintercept = .20, colour ="red")+scale_y_continuous(breaks=c(5,50,100,200), limits = c(0, 200))

F2.iic2 <- ggplot(F2.item.info.data.2,aes(Theta,value,col=variable))+geom_line()+apatheme+
  ggtitle("F2 Item Information Plot")+theme(legend.position = "none")+
  labs(y = "Item Information")+facet_wrap(~variable)+theme(strip.text.x = element_text(size = 15))+
  scale_color_npg()+geom_hline(yintercept = .20, colour ="red")

F3.iic2 <- ggplot(F3.item.info.data.2,aes(Theta,value,col=variable))+geom_line()+apatheme+
  ggtitle("F3 Item Information Plot")+theme(legend.position = "none")+
  labs(y = "Item Information")+facet_wrap(~variable)+theme(strip.text.x = element_text(size = 15))+
  scale_color_npg()+geom_hline(yintercept = .20, colour ="red")

F4.iic2 <- ggplot(F4.item.info.data.2,aes(Theta,value,col=variable))+geom_line()+apatheme+
  ggtitle("F4 Item Information Plot")+theme(legend.position = "none")+
  labs(y = "Item Information")+facet_wrap(~variable)+theme(strip.text.x = element_text(size = 15))+
  scale_color_npg()+geom_hline(yintercept = .20, colour ="red")

F5.iic2 <- ggplot(F5.item.info.data.2,aes(Theta,value,col=variable))+geom_line()+apatheme+
  ggtitle("F5 Item Information Plot")+theme(legend.position = "none")+
  labs(y = "Item Information")+facet_wrap(~variable)+theme(strip.text.x = element_text(size = 15))+
  scale_color_npg()+geom_hline(yintercept = .20, colour ="red")

ICC2 <- cowplot::plot_grid(vic.iic2 , agg.iic2,  labels = "AUTO",ncol=2, label_size = 15,align = "v")
ggsave("Figures/ICC2.jpeg",ICC2 , width = 12, height = 8, dpi = 1200, bg = "white")

@@

F1.tic <- ggplot(F1.test.data, aes(x=Theta, y=F1.T1)) +
  geom_line()+apatheme+
  labs(y="Test Information", title = "F1 Test Inforfamtion")+scale_color_brewer(palette="Dark2")

@@

TIC <- cowplot::plot_grid(F1.tic,F2.tic, F3.tic,
                                   F4.tic,F5.tic,
                   labels = "AUTO",
                     align="v",
                     ncol = 2,
                     label_size = 15,
                     label_fontfamily = "Arial",
                     label_fontface = "plain")
ggsave("Manuscript.figures/TIC.png",TIC, width = 10, height = 12, dpi = 1200, bg = "white")

@@

```{r perfit, include=F}
personfit <- plot_grid(F1.person, F2.person,F3.person,F4.person,F5.person, 
          labels = "AUTO", label_size = 12,align = "v", ncol =2,
                       label_fontfamily = "Arial",
                     label_fontface = "plain")
